Improving Day Ahead Electricity Load Forecasts with Google Trends

### 2014-07-28 Paper/DraftPaper.Rnw
Added all the needed calculations from ResearchNotes.Rmd

<<echo=FALSE,results=hide>>=
load("~/Research/Forecast-Peak-With-Google-Trends/DataManipulation/WTrends")
@

@@

  \subsection{PJM Load Forecasts and Actuals}

@@

@@

@@

  \subsection{Counter-factual Test with Other Common Google Searches}
    \begin{enumerate}
      \item Comparison with: news, recipe, traffic, gas.
      \item Note that some of them kinda work.
    \end{enumerate}

>>>>

<<echo=FALSE,results=hide>>=
load("~/Research/Forecast-Peak-With-Google-Trends/DataManipulation/WTrends")

WTrends$Weather<-((925749*WTrends$DETrends)+(4395295*WTrends$KYTrends)+(5928814*WTrends$MDTrends)+(8899339*WTrends$NJTrends)+(11570808*WTrends$OHTrends)+(12773801*WTrends$PATrends)+(8260405*WTrends$VATrends)+(1854304*WTrends$WVTrends))/(925749+4395295+5928814+8899339+11570808+12773801+8260405+1854304)  
@

@@

  \subsection{PJM Load Forecasts and Actuals}
<<>>=
HourModelForecastCheck<-function(hour){
  Hour<-formatC(hour, width=2, flag="0")
  as.formula(paste("HE",Hour,"~ F",Hour,sep='' ))}

SAResults<-lapply(1:24, FUN = function(x)  lm(HourModelForecastCheck(x), data=WTrends))

@

@@

<<echo=false,results=hide>>=
WTrendsLimited<-WTrends[!is.na(WTrends$Weather),]

HourModel<-function(hour){
  Hour<-formatC(hour, width=2, flag="0")
  as.formula(paste("HE",Hour,"~ F",Hour,"+Weather",sep='' ))}

# Gives percent reduction in sigma
CompareRaw<-function(x){
SA<-sd(WTrendsLimited[,x]-WTrendsLimited[,30])  
Google<-summary(lm(HourModel(x), data=WTrendsLimited))$sigma

(SA-Google)/(SA)
}

lapply(1:24, FUN = CompareRaw)
mean(unlist(lapply(1:24, FUN = CompareRaw)))

@

<<echo=false,results=hide>>=
HourModel<-function(hour){
  Hour<-formatC(hour, width=2, flag="0")
  as.formula(paste("HE",Hour,"~ F",Hour,"+Weather",sep='' ))}

GrossTrends<-lapply(1:24, FUN = function(x)  lm(HourModel(x), data=WTrends))
@

<<echo=false,results=hide>>=

# Gives percent reduction in sigma
CompareSigma<-function(x){
SA<-summary(lm(HourModelForecastCheck(x), data=WTrendsLimited))$sigma  
Google<-summary(lm(HourModel(x), data=WTrendsLimited))$sigma

(SA-Google)/(SA)
}

lapply(1:24, FUN = CompareSigma)
mean(unlist(lapply(1:24, FUN = CompareSigma)))

@

@@

<<echo=false,results=hide>>=

OneForwardError<-function(formula, nData){
  model<-lm(formula, data=WTrendsLimited[1:nData,], y=TRUE)
  modelPlus1<-lm(formula, data=WTrendsLimited[1:(nData+1),], y=TRUE)
  predict(model,WTrendsLimited[1+nData,])-tail(modelPlus1$y,1)
}

CVDropForward<-function(model){sd(unlist(lapply(20:(length(WTrendsLimited)-1), FUN= function(x) OneForwardError(model,x))))}

CompareSigmaCV<-function(x){
SA<-CVDropForward(HourModelForecastCheck(x))  
Google<-CVDropForward(HourModel(x))

(SA-Google)/(SA)
}

CVImprove<-lapply(1:24, FUN = CompareSigmaCV)
CVImprove
mean(unlist(CVImprove))
@

@@

  \subsection{Counter-factual Test with Other Common Google Searches}

    \begin{enumerate}
      \item Comparison with: news, recipe, traffic, gas.
      \item Note that some of them kinda work.
    \end{enumerate}

<<echo=false,results=hide>>=
summary(lm(HE19~F19+NewsTrends,data=WTrends))
# Oh, that works too
summary(lm(HE19~F19+GasTrends,data=WTrends))
# Gas does not
summary(lm(HE19~F19+TrafficTrends,data=WTrends))
# Traffic does not
summary(lm(HE19~F19+RestaurantTrends,data=WTrends))
# Restaurant does not
summary(lm(HE19~F19+MovieTrends,data=WTrends))
# Snort...Movie does.  Cool place to be.
@
